Measuring Perceptions and Preferences for Meritocracy

### 2021-06-11 paper_study1.Rmd

```{r meas02-issp, echo=FALSE, fig.cap = "Descriptive plot", fig.align='center',fig.cap="Meassurement model for Perceptions and Preferences in meritocracy"}
knitr::include_graphics('output/images/meas02-issp.PNG')
```

>>>>

```{r meas02-issp, echo=FALSE, fig.cap = "Descriptive plot", fig.align='center',fig.cap="Confirmatory factor analysis of the Perceptions and Preferences for Meritocracy"}
knitr::include_graphics('output/images/cfa_issp_study1.PNG')
```
